%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Systems \& Software (Harris Computer)}{May 2021 -- Current}
    {Team Lead, R\&D}{Philadelphia, Pennsylvania (Remote)}
    \resumeItemListStart
        \resumeItem{Managed team of programmers. Performing yearly performance reviews and helping work on goals/career development.}
        \resumeItem{Acted as mentor for newer developers, helping create understanding of the tech stack and build problem solving skills to be able to act independently.}
        \resumeItem{Worked with senior management to refine interview process for new groups of programmers being hired to work remotely. Led technical interviews and reviewed programming skills tests to filter candidates. Once candidates were hired helped build new training material to get them up to speed in a short time frame.}
        \resumeItem{Worked to implement agile practices such as code review and scrum helping to lower QA failure rate for developers and increase code quality.}
        \resumeItem{Acted as Technical PM/Dev Lead for a project to add a new feature that was needed for a demo. Worked within tight timeline, organized work and made sure communication was flowing to meet goals on time.}
        \resumeItem{Acted as Consultant and Developer for multiple integrations between product and other systems. Leading discussions, helping vendors understand documentation, assisting in problem solving and architecture.}
        \resumeItem{Reverse-engineered existing DevOps code to find places where alterations could be made to enhance the speed of deployments. Refactored and documented code as this was completed.}
        \resumeItem{Acted as technical point of contact on multiple software upgrades. Reviewed issues incoming from project to see whether or not they required development. Communicated with customer to explain technical issues when needed.}
        \resumeItem{Implemented interface for existing software processes to be refactored into Jakarta EE Batch Jobs. Created RESTful API to query status of batch jobs. Allowing existing long running synchronous web calls to be made asynchronous.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Systems \& Software (Harris Computer)}{July 2018 - May 2021}
    {Software Engineer, Support}{Winooski, Vermont}
    \resumeItemListStart
        \resumeItem{Maintained Utility CIS software, working on full stack to fix bugs tracked in support tickets. Application stack including COBOL, Java, JavaScript, and Oracle.}
        \resumeItem{Directly managed multiple accounts from a support perspective. Met regularly with clients to ensure tickets were being handled appropriately and needs were being met.}
        \resumeItem{Performed Root Cause Analysis for critical system failure events. Reviewing logs, heap+thread dumps, and system monitoring data to discover causes behind issues and prevent future occurrences.}
        \resumeItem{Did analysis of customer relationship for customer that was having issues after moving to a newer version of the software. Went through multiple months of tickets to call out common system bugs and issues that needed to be resolve. Also called out key people from the customer side and their pain points.}
    \resumeItemListEnd

    \resumeSubheading
    {CSL Software Solutions}{February 2017 - June 2018}
    {Lead Application Developer}{Burlington, Vermont}
    \resumeItemListStart
        \resumeItem{Developed and maintained web applications for data entry and reporting. Used technologies such as ExtJS, DevExtreme, WCF, and SQL Server.}
        \resumeItem{Lead development of new multi-lingual offline web application for sales coaching. Worked to implement app with client teams in NA (US) and EU (UK, Belgium).}
        \resumeItem{Mentored other team members, guiding them through projects they were working on helping to maintain on time delivery.}
    \resumeItemListEnd

\resumeSubHeadingListEnd